\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-28 metatheory-condensed.tex
Wrec

\noindentparagraph{W-types.}

W-types~\cite{martin1984intuitionistic} are a standard way to model
inductive types in MLTT.
A constructor of some inductive type~$T$ is given by a pair of types
$\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$ (rule \ruleref{wsig/add}):
given two arguments $\goodTerm{\Gm}{t_1}{A}$ and
$\goodTerm{\Gm,\sub{B}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{T}$,
it constructs a term of type~$T$ (rule \ruleref{tm/wsup}).
As the rules suggest, our formulation additionally supports
\emph{W-type signatures} (judgment form \goodWSig{\Gm}{\wsig}{n})
composed of $n$ pairs of types, each of which represents a constructor.

>>>>

\noindentparagraph{Introducing and eliminating inductive types.}

W-types~\cite{martin1984intuitionistic} are a standard way to model
inductive types in MLTT.
A constructor of an inductive type~$T$ is given by a pair of types
$\goodType{\Gm}{A}{}$ and $\goodType{\Gm,A}{B}{}$ (\ruleref{wsig/add}):
given two arguments $\goodTerm{\Gm}{t_1}{A}$ and
$\goodTerm{\Gm,\sub{B}{\SubstExt{\SubstWeak{0}}{t_1}}}{t_2}{T}$,
it constructs a term of type~$T$ (\ruleref{tm/wsup}).
As the rules suggest, our formulation additionally supports
\emph{W-type signatures} (judgment form \goodWSig{\Gm}{\wsig}{n})
composed of $n$ pairs of types, each of which represents a constructor.

W-types are eliminated by $\Wrec{\lkg}{t}$, where $t$ is of the W-type
$\El{\wcode{\wsig}}$, and $\lkg$ is essentially an $n$-tuple of case
handlers for the $n$ constructors in~$\wsig$ (\ruleref{tm/wrec}).
The type of each case handler has the form $\CaseSig{A}{B}{T}$, where
$T$ is the motive of the recursion (\ruleref{ty/casety}).
This collection of case handlers then encodes the \lsti{FRecursion}
construct supported by our plugin.
We choose to give it a linkage type $\TyLkg{\RecSig{\wsig}{T}}$,
but it could be typed as an ordinary $n$-tuple, which is subsumed by
linkages to be introduced next.

\noindentparagraph{Linkages.}
